\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-08-11 paper/paper.tex
Work on references
Clean up appendix

\subsection{Computation}
\label{sec:Computation}
Each model was fit using the {\tt
  rstan}\cite{rstan} package in {\tt R} \cite{r}, which implements a variant of Hamiltonian Monte Carlo (HMC)
\cite{betancourt}. HMC jointly updates all model parameters by simulating paths along the posterior density. This is done to reduce autocorrelation and efficiently explore the posterior. Multiple chains were run for 1500 iterations after 1500 warmup iterations: 4 chains were run for Models 1,2 and 3 and 16 chains were run for Model 4. The Gelman-Rubin potential scale reduction factors, ``R-hat", which test for lack of convergence by comparing the between versus within chain variability were used. Upon convergence, R-hat converges to 1. For the four model fits, the  maximum values over all the model parameters were 1.005, 1.028, 1.009 and 1.004, respectively. The minimum estimated effective sample size over all the model parameters for the four model fits were 567, 205, 672 and 3330, respectively. No divergent transitions occurred after warmup.

@@

%Hierarchical modeling can be an effective way to regularize a large number of models fits by borrowing information.  %Because all the data contribute some information about the global parameters, it is often sufficient to use weakly %informative priors on the global parameters, making the resulting shrinkage data dependent.  Analysis using HMC is %accessible to practitioners by Stan. HMC has been shown to be very efficient in effective samples per iteration because %its joint updating scheme.

\section{Appendix}
\label{sec:Appendix}
We first start with a non-parametric estimate of the empirical cdf for each drive-model using the Kaplan-Meier estimator
\cite{kaplan}.  With left truncation, however, the standard Kaplan-Meier estimator for drive-model $d$, denoted by
$\widehat{F_d(t)}_{KM}$, is conditional on survival up to
$t_{d,\text{min}}^L$, the shortest reported running time of all units
of drive-model $d$ for which records are available. To produce
unconditional estimates, we adapt the adjustment method outlined by
Turnbull, and given in more detail by Meeker and Escobar
\cite{turnbull,meeker}.  For each drive-model we select
$t_{d,\text{min}}^L$, the smallest left truncated time in the sample.
By sampling from the full posterior distribution, since
$\Pr(T>t_{d,\text{min}}^L|\theta_d)$ (the probability a hard drive has
survived up to $t_{d,\text{min}}^L$) is a function of the model
parameters, we can easily compute its posterior median,
$\widehat{A}_{\text{med}} = \widehat{Pr}(T>t_{d,\text{min}}^L|\theta_d)$. We compute the adjusted estimate by

@@

\begin{center}
{\large\bf SUPPLEMENTARY MATERIAL}
\end{center}

\begin{description}

\item Put R Stan code here

\end{description}

\begin{appendix}
\scriptsize
\begin{verbatim}
functions {
  real sev_logpdf(real y, real mu, real sigma){
    real z;
    z = (y - mu) / sigma;
    return -log(sigma) + z - exp(z);
  }

@@

\end{verbatim}
\end{appendix}

@@

\bibliographystyle{plainnat}
%\bibliographystyle{apalike}
\bibliography{sample}

>>>>

\subsection{Computation}
\label{sec:Computation}
Each model was fit using the {\tt
  rstan}\cite{rstan} package in {\tt R} \cite{r}, which implements a variant of Hamiltonian Monte Carlo (HMC)
\cite{betancourt}. HMC jointly updates all model parameters by simulating energy preserving paths with random initial momentums along the posterior density. This is done to reduce autocorrelation and efficiently explore the posterior. Multiple chains were run for 1500 iterations after 1500 warmup iterations: 4 chains were run for Models 1,2 and 3 and 16 chains were run for Model 4. The Gelman-Rubin potential scale reduction factors, ``R-hat", which test for lack of convergence by comparing the between versus within chain variability were used. Upon convergence, R-hat converges to 1. For the four model fits, the  maximum values over all the model parameters were 1.005, 1.028, 1.009 and 1.004, respectively. The minimum estimated effective sample size over all the model parameters for the four model fits were 567, 205, 672 and 3330, respectively. No divergent transitions occurred after warmup.

@@

%Hierarchical modeling can be an effective way to regularize a large number of models fits by borrowing information.  %Because all the data contribute some information about the global parameters, it is often sufficient to use weakly %informative priors on the global parameters, making the resulting shrinkage data dependent.  Analysis using HMC is %accessible to practitioners by Stan. HMC has been shown to be very efficient in effective samples per iteration because %its joint updating scheme.  
\clearpage

\appendix
\section{Truncation adjusted nonparametric estimate of lifetime}
\label{sec:trunc-adj}
We first start with a non-parametric estimate of the empirical cdf for each drive-model using the Kaplan-Meier estimator
\cite{kaplan}.  With left truncation, however, the standard Kaplan-Meier estimator for drive-model $d$, denoted by
$\widehat{F_d(t)}_{KM}$, is conditional on survival up to
$t_{d,\text{min}}^L$, the shortest reported running time of all units
of drive-model $d$ for which records are available. To produce
unconditional estimates, we adapt the adjustment method outlined by
Turnbull, and given in more detail by Meeker and Escobar
\cite{turnbull,meeker}.  For each drive-model we select
$t_{d,\text{min}}^L$, the smallest left truncated time in the sample.
By sampling from the full posterior distribution, since
$\Pr(T>t_{d,\text{min}}^L|\theta_d)$ (the probability a hard drive has
survived up to $t_{d,\text{min}}^L$) is a function of the model
parameters, we can easily compute its posterior median,
$\widehat{A}_{\text{med}} = \widehat{Pr}(T>t_{d,\text{min}}^L|\theta_d)$. We compute the adjusted estimate by

@@

% \begin{center}
% {\large\bf SUPPLEMENTARY MATERIAL}
% \end{center}
% 
% \begin{description}
% 
% \item Put R Stan code here
% 
% \end{description}

\section{Stan code for model 4}
\label{sec:stan-code}
{\scriptsize
\begin{verbatim}
functions {
  real sev_logpdf(real y, real mu, real sigma){
    real z;
    z = (y - mu) / sigma;
    return -log(sigma) + z - exp(z);
  }

@@

\end{verbatim}
}

@@

% \bibliographystyle{plainnat}
\bibliographystyle{apalike}
\bibliography{sample}
